On the error performance of the $A_n$ lattices

### 2011-11-11 paper.tex
Added back Emanuele's abstract, title and keywords.

%\documentclass[a4paper,10pt]{article}
\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal]{../bib/IEEEtran}
%\documentclass[correspondence,9pt]{../bib/IEEEtran}

@@

@@

\begin{figure*}[tp]
	\centering
		\includegraphics{plots/peplots-1.mps}
		\caption{The probability of error versus SNR for $A_1 \simeq \ints$, $A_2$, $A_3\simeq D_3$, $A_4$, $E_8$ and the Leech lattice $\Lambda_{24}$.}
		\label{fig:peplots}
\end{figure*}

>>>>

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
\documentclass[journal]{IEEEtran}
%\documentclass[correspondence,9pt]{IEEEtran}

@@

Given a lattice with inradius $\rho$ and Voronoi cell having volume $V$ we define the SNR as
\[
\frac{n^2 \sigma^2 V_n}{(n+2)(\log(V_n) - \log(V) + n\log(\rho))}
\]
where $V_n$ is the volume of the $n$ dimensional hypersphere and the logarithms are base $2$.

@@

\begin{figure*}[tp]
	\centering
		\includegraphics{plots/peplots-1.mps}
		\caption{The probability of error versus SNR for $A_1 \simeq \ints$, $A_2$, $A_3\simeq D_3$, $A_4$, and $A_5$ and $E_8$ and the Leech lattice $\Lambda_{24}$.}
		\label{fig:peplots}
\end{figure*}
